---
title: "Moses Martin Njuguna Gikonyo"
date: "`r Sys.Date()`"
description: |
  Data Scientist | Quantitative Financial Engineer | Frontier Market Intelligence
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About Me

I am a Data Scientist and Quantitative Financial Engineer based in Nairobi, Kenya, operating at the intersection of machine learning, quantitative finance, and frontier market intelligence. I completed an **Applied Data Science** programme and am commencing my **MSc in Financial Engineering at WorldQuant University** in April 2026.

My work is defined by rigour, systems thinking, and a commitment to building production-grade analytical frameworks — not just models, but deployable intelligence systems.

---

## Current Research

I am currently building a **Frontier Market Regime Classification Framework**, with a live operational node in Baku. This project applies advanced machine learning techniques to classify macroeconomic and market regimes across frontier and emerging markets — an underserved space in quantitative research with significant alpha generation potential.

**Core methods include:**

- Hidden Markov Models (HMM) for regime detection
- Bayesian inference for uncertainty quantification
- Time-series feature engineering across macroeconomic indicators
- Live data pipeline with a Baku node for real-time regime signals

---

## Selected Projects

### Churn Analytics SaaS
A PostgreSQL-backed churn analytics platform incorporating retention modelling, survival analysis, and LTV estimation. Built for production deployment using Python.

### Customer Lifetime Value Platform
A production-grade CLV analytics system built with SQL, Python, R, Docker, and Kubernetes — designed for enterprise-scale customer intelligence.

### Bayesian Incrementality & Geo-Lift
Bayesian causal inference framework for measuring true marketing incrementality using geo-based experiments — separating signal from noise in marketing attribution.

### A/B Testing & Senior Experimentation Framework
An end-to-end experimentation platform for rigorous A/B testing, designed to meet senior-level statistical standards across product and growth teams.

### Funnel & Growth Analytics Platform
A FAANG-style funnel and growth analytics platform built with PostgreSQL, SQL, Python, R, Docker, and Kubernetes.

---

## Teaching & Lecture Materials

I launched this site in 2021 as an educational resource for those beginning their journey in R and data science. Below is an example from **Lecture 1**, introducing the `gapminder` dataset — a powerful tool for understanding global development trends through visual exploration.

### Lecture 1 — Exploring Global Development with Gapminder

The `gapminder` library in R provides clean, curated data on GDP per capita, life expectancy, and population across countries and time. It is an excellent entry point for learning data visualisation and exploratory data analysis.

The chart below plots **GDP per capita against life expectancy in 1977**, with bubble size representing population and colour representing continent. It raises a fundamental question in development economics: does wealth buy longevity?
```{r gdpplot, eval=TRUE, echo=FALSE, fig.cap="GDP per Capita vs Life Expectancy by Continent (1977)"}
library(tidyverse)
library(gapminder)

p <- gapminder %>%
  filter(year == 1977) %>%
  ggplot(aes(x = gdpPercap, y = lifeExp, size = pop, color = continent)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(labels = scales::comma) +
  labs(
    x = "GDP per Capita (log scale)",
    y = "Life Expectancy (years)",
    size = "Population",
    color = "Continent",
    title = "Wealth vs Longevity Across Nations (1977)"
  ) +
  theme_bw()
p
```

**Discussion Questions:**

1. Which countries demonstrate the strongest correlation between economic growth and increasing life expectancy?
2. Does a higher GDP per capita reliably predict greater longevity — and where does this relationship break down?

---

## Technical Stack

| Domain | Tools |
|---|---|
| Languages | R, Python, SQL |
| ML & Stats | scikit-learn, tidymodels, Stan, HMM |
| Data Engineering | PostgreSQL, Docker, Kubernetes |
| Visualisation | ggplot2, Plotly, Matplotlib |
| Finance | Quantitative modelling, regime classification |
| Reporting | R Markdown, Distill, Quarto |

